NEED TITLE

### 2014-12-02 ms.tex
rearranged plots and update text

We have also implemented a new algorithm for mesh refinement in these simulations.  As gas collapse under self gravity, certain regions rapidly increase in density.  These regions are refine when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\begin{equation}
refinement criteria
\end{equation}
which when met causes the local grid to be refined by a factor of 2 provide that the maximum refinement level is not reached.

@@

The high density regions appear to be organized along filaments.  These filaments span most of the simulation size, and have a width of 0.5 to 1 pc.  Moreover, these filaments appear to flow into large clumps.  This is in line with previous work including Lee et al. 2014.

The simulated volume has a large number of refined regions.  We show three of them in Figure \ref{fig:snapshots} as slices perpendicular to the angular momentum vector.  We determine the angular momentum vector by taking a $0.01$ pc region about the densest local point and calculate the angular momentum vector.  We also so a zoom out picture of the same region, which is the same for all three stars.  While this is not unexpected as star formation is clustered, the large scale dynamics are determined by the larger region.

A second family of two star particles were found in our simulation, show im Figure \ref{fig:snapshots 2}.  Here again we show a zoom in and zoom out picture, comparing detail between the two particles around an axis of the angular momentum.  Again the zoom in plots show two distinct star forming regions, while the zoom-out plot show that the larger region and hence large scale dynamics are the same.

\begin{figure*}
\plottwo{Disk_0132_0000.png}{Disk_0132_0002.png}
\caption{Cut of the two star forming regions.}
\end{figure*}

@@

The zoom in plots in Figures \ref{fig:snapshots} and \ref{fig:snapshots 2} suggest that the accretion can occur by streams or by spherical flows.  However, the degree by which these modes of accretion dominate, is not clear.  At small radii (similar to $10^{-2}$ pc), a protostellar disk appears in all four snapshots. The radial size of these disks varies. These disks also show a coherent sense of rotation about a common axis, e.g., no counter-rotating disks. In addition, some of the snapshots show multiple high density regions.  This could be a result of accretion of high density clumps or fragmentation in the disk or streams.

\subsection{Examples of Collapse}

>>>>

We have also implemented a new algorithm for mesh refinement in these simulations.  As gas collapse under self gravity, certain regions rapidly increase in density.  These regions are refine when the Truelove criterion ($\lambda \le 4 \Delta x$) is met. This corresponds to a condition on the density 
\begin{equation}
refinement criteria
\end{equation}
which when met causes the local grid to be refined by a factor of 2 provided that the maximum refinement level is not reached.

@@

The high density regions appear to be organized along filaments.  These filaments span most of the simulation size, and have a width of 0.5 to 1 pc.  Moreover, these filaments appear to flow into large clumps.  This is in line with previous work including Lee et al. 2014. These clumpy regions have the highest densities and, hence, are prone to fulfill the criterion for star particle formation.

At the instance in time shown in Figure \ref{fig:entire projection}, a total of five star particles have been formed.  However, these star particles are not formed in isolation.  Rather they congregate in two star forming regions shown in Figure \ref{fig:star forming regions}.  In these regions, the sink particles that are formed lay within 0.1 pc of one another, which reflects that the highest density regions are concentrated toward the center.  Visually, the character of accretion at the this outer scale appear to flow along filaments, thought previous work (Lee et al. 2014) has shown that the majority of accretion is spherical.  We discuss this more quantitatively below {\bf INCLUDE A STUDY OF LARGE SCALE ACCRETION}

\begin{figure*}
\plottwo{Disk_0132_0000.png}{Disk_0132_0002.png}
\caption{Cut of the two star forming regions.\label{fig:star forming regions}}
\end{figure*}

The first family of three star particles is shown in Figure \ref{fig:snapshots} and the second family of two star particles is shown in Figure \ref{fig:snapshots 2}.  We plot these particles and their surrounding $4\times 10^{-2}$ pc region as slices perpendicular to the local angular momentum vector.  We determine the local angular momentum vector by taking a $0.01$ pc region about the star particle to calculate the angular momentum vector.  It is clear from these plots that the clumpy filamentary nature of the local star forming environment extends down to much smaller scales than we have been able to probe in previous work (Lee et al. 2014).

{\bf INCLUDE ACCRETION TOPOLOGY STUDY HERE.}

At small radii (similar to $10^{-2}$ pc), a protostellar disk appears in all five snapshots. The radial size of these disks varies. These disks also show a coherent sense of rotation about a common axis, e.g., no counter-rotating disks. In addition, some of the snapshots show multiple high density regions.  This could be a result of accretion of high density clumps or fragmentation in the disk or streams.

We also include a zoom-out picture of the same region, which is the same for all three stars (lower right plot in Figure \ref{fig:snapshots}, bottom plot in Figure \ref{fig:snapshots 2}).  While this is not unexpected as star formation is clustered, the large scale dynamics are determined by the larger region.  We should note that these star particles are within about 0.1 pc of each other in their respective families.

{\bf ARE THESE DISK GRAVITATIONALLY STABLE?}

@@

\subsection{Radial Profile of Collapse}
